\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumerate}
\usepackage{comment}

%Title
\title{Second Weekly Report}
\author{Team05}
\date{November 12, 2018}

\begin{document}

\begin{titlepage}
\maketitle
\end{titlepage}

This week is week 8 for this semester (November 7, 2018). For this week we focus on the requirements from the stakeholder, and do some research for it.\\


For this week, we had multiple tasks to get done. We had to draw use case diagram, low fidelity prototypes, mind map, add contents to our interim report outline, and weekly research about existing tools relevant to our project. The  use-case diagram was drawn to identify application functionalities and to represent roles of the actors that are played by the users of the app. It was drawn using papyrus. Mind map was designed using mind line as it is a convenient tool for brainstorming. For prototype illustration, tool that has been used is xiaopiu (a software can do both low and high fidelity prototypes) where several optional templates were provided.\\


 According to the new requirements given, security and payment methods were two essential functionalities the client was mostly concerned about. For payment methods, we looked at how to integrate payment gateway in the app. PayPal and Alipay were specifically noted in the requirements as the chosen payment methods. For Paypal, there’s a transaction fee of 2.9 per cent of the transfer sum plus USD0.30 and set up account fee. Additionally, Paypal charges a monthly subscription of USD35. We also looked into some of its features, such as receiving report of your financial activity. For Alipay, we can provide filmmaker’s QR in which the viewer can scan and be redirected to the Alipay app.\\
 
 
Additional requirement is, the uploaded films should be secured in a way that no user should be able to download films. Thus, the client mentioned blockchain as a measure of security to consider. So, we are researching more about it and still trying to figure out how to use this technology. Blockchain provides two main features that are relevant to the app. First feature is, it does not allow any breach of data. Secondly, it boost transaction’s security. Moreover, we looked into CMS which can be accessed through the backend of a website and allows the admin to alter any changes to the contents in the app. We prioritized few of the requirements and searched how we can provide proof of concept. For instance, adding security methods as it is a key feature which has an increased risk.\\

To sum up, we concluded to use eclipse JDK to code for the android version as we are familiar with the software.



\end{document} 