\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumerate}
\usepackage{comment}
\usepackage{url}
%\usepackage{hyperref}
%Title
\title{Third Weekly Report}
\author{Team05}
\date{2018, November 12}

\begin{document}

\begin{titlepage}
\maketitle
\end{titlepage}

This week is week 9 for this semester (2018, November 7). For this week we focus on the requirements from the stakeholder, and do some research for it.And we had multiple tasks to get done. We add some animation effects and jump function in low fidelity prototypes,draw new mind map for requirements, and weekly research about existing tools and technology relevant to our project.\\

\begin{enumerate}[1.]
  \item Security\cite{bitmovin}\\
  One of Alex’s biggest concern is viewers pirating films from the app. This could lead to filmmakers withdrawing their film and discourage other filmmakers to use theshortfilmshow app as a safe platform to show their film. Nowadays, app developers use DRM as a method to secure their app. Digital rights management (DRM) is a systematic approach to copyright protection for digital media. The use of DRM is to prevent unauthorized redistribution of the films and restrict the ways viewers can copy films they've purchased. DRM was purposely developed in response to the increased number of online piracy. It uses scheme such as PlayReady. However, implementation of DRM is quite complex as it requires creating own licensing server and implement specification to allow integration with DRM chain, such as encoding.\\
  \item Development tools\cite{APICloud}\\
  To develop a cross platform app with only one codebase, we came across APICloud which be used in develop a web app. APICloud provides comprehensive tools and tutorials for guidance.\\
  But if we want to have more fast application, navite app is better choice. At that time, Android Studio is good tools to our development for Android version.\\
  \item Blockchain\cite{blockchain}\\
  Definition: in a narrow sense, blockchain is a kind of chain data structure composed of data blocks connected sequentially in a chronological order, and it is guaranteed to be tamper able and unfalsifiable distributed ledger in a cryptographic way. Generalized block chain technology is using block chain to verify the data structure and data storage, the use of distributed node consensus algorithm to generate and update the data, the use of cryptography way to ensure the security of data transmission and access, the use of automated script code intelligent contracts to programming and operating data of a new distributed infrastructure and computing paradigm.\\

Objective: to solve the problem of intermediary credit\\

But for our short movie application, we force on security and privacy of data. It is no way to share all data with everyone. So, we think blockchain is not necessary technology in our software development.

  \item CMS\\
  After Meeting with Alex, We get a CMS which be used in shortfilmshow named filmfreeway.
\end{enumerate}

\bibliographystyle{abbrv}
\bibliography{weekly_report}


\end{document} 